---
title: "Redefining Marketing Research: Data Science & AI"
author: "Group 10 - Eder Garcia, Dusty Vela"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE,
  fig.align = "center", fig.width = 9, fig.height = 5
)

packages <- c("ggplot2", "dplyr", "tidyr", "scales",
              "knitr", "kableExtra", "patchwork", "stringr")
for (pkg in packages) {
  if (!require(pkg, character.only = TRUE, quietly = TRUE))
    install.packages(pkg, quiet = TRUE)
  library(pkg, character.only = TRUE)
}

colors <- c("#2C3E7A", "#E84393", "#00BFFF", "#7B2FBE", "#F97316", "#10B981")

# ── Load data ──────────────────────────────────────────────────────────────
df <- read.csv("marketing_research_data.csv", stringsAsFactors = FALSE)
get_ds <- function(name) df %>% filter(dataset == name)

revenue_global  <- get_ds("01_revenue_global")
revenue_region  <- get_ds("02_revenue_region")
top_companies   <- get_ds("03_top_empresas")
porters         <- get_ds("04_porters_five_forces")
methods         <- get_ds("05_metodos_investigacion")
rev_service     <- get_ds("06_revenue_por_servicio")
response_hist   <- get_ds("07_tasas_respuesta_historico")
response_comp   <- get_ds("08_tasas_respuesta_comparacion")
ai_function     <- get_ds("09_ia_adopcion_funcion")
ai_kpis         <- get_ds("10_ia_marketing_research_kpis")
ai_market       <- get_ds("11_ia_mercado_proyeccion")
kpis_summary    <- get_ds("12_kpis_resumen")
```

---

# Introduction

This document provides a quantitative analysis of the global **Marketing Research** industry
and its ongoing transformation toward **Data Science**. All data were compiled from ESOMAR,
Statista, McKinsey, Qualtrics, and The Business Research Company (2022–2025).

> *"Data science is fast becoming the new look of marketing research."*
> — Miller, Modeling Techniques in Predictive Analytics

---

# Global Industry Growth

## Global Revenue 2008–2024

```{r revenue-global}
revenue_global$year       <- as.integer(revenue_global$year)
revenue_global$revenue_bn <- as.numeric(revenue_global$revenue_bn)

ggplot(revenue_global, aes(x = year, y = revenue_bn)) +
  geom_area(fill = colors[1], alpha = 0.15) +
  geom_line(color = colors[1], linewidth = 1.5) +
  geom_point(color = colors[1], size = 2.5) +
  geom_point(data = revenue_global %>% filter(year == 2024),
             color = colors[2], size = 5) +
  annotate("text", x = 2023.2, y = 145,
           label = "$140B (2024)", color = colors[2], fontface = "bold", size = 4) +
  annotate("text", x = 2010, y = 35,
           label = "$29.5B (2009)", color = colors[1], fontface = "bold", size = 3.5) +
  scale_x_continuous(breaks = seq(2008, 2024, by = 2)) +
  scale_y_continuous(labels = dollar_format(suffix = "B", prefix = "$")) +
  labs(
    title    = "Global Market Research Industry Revenue (2008–2024)",
    subtitle = "Over 380% growth in 16 years | Source: ESOMAR",
    x = "Year", y = "Revenue (USD Billions)"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title       = element_text(face = "bold", size = 14, color = "#1A1A2E"),
    plot.subtitle    = element_text(color = "gray40", size = 10),
    panel.grid.minor = element_blank()
  )
```

## Revenue by Region (2022)

```{r revenue-region}
revenue_region$share_pct  <- as.numeric(revenue_region$share_pct)
revenue_region$revenue_bn <- as.numeric(revenue_region$revenue_bn)

# Translate region names
revenue_region$region_en <- dplyr::recode(revenue_region$region,
  "Norteamérica"           = "North America",
  "Europa"                 = "Europe",
  "Asia-Pacífico"          = "Asia-Pacific",
  "Latinoamérica"          = "Latin America",
  "Medio Oriente & África" = "Middle East & Africa"
)
revenue_region$region_en <- factor(revenue_region$region_en,
  levels = revenue_region$region_en[order(revenue_region$share_pct)])

ggplot(revenue_region, aes(x = region_en, y = share_pct, fill = region_en)) +
  geom_col(width = 0.65, show.legend = FALSE) +
  geom_text(aes(label = paste0(share_pct, "%\n($", revenue_bn, "B)")),
            hjust = -0.1, size = 3.5, fontface = "bold") +
  scale_fill_manual(values = rev(colors)) +
  scale_y_continuous(limits = c(0, 65)) +
  coord_flip() +
  labs(
    title    = "Global Revenue Distribution by Region (2022)",
    subtitle = "North America accounts for over 50% of the market | Source: Statista",
    x = NULL, y = "Market Share (%)"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title         = element_text(face = "bold", size = 14, color = "#1A1A2E"),
    plot.subtitle      = element_text(color = "gray40", size = 10),
    panel.grid.major.y = element_blank()
  )
```

## Top Companies by Revenue

```{r top-companies}
top_companies %>%
  transmute(
    Company            = empresa,
    Country            = pais,
    `Research Revenue` = paste0("$", revenue_research_bn, "B"),
    Year               = year,
    Specialty          = especialidad
  ) %>%
  kable(align = c("l","c","c","c","l"),
        caption = "Top Global Market Research Companies | Source: Statista / ESOMAR 2022") %>%
  kable_styling(bootstrap_options = c("striped","hover","condensed","responsive"),
                full_width = TRUE) %>%
  column_spec(1, bold = TRUE, color = colors[1]) %>%
  column_spec(3, bold = TRUE, color = colors[2]) %>%
  row_spec(0, background = colors[1], color = "white", bold = TRUE)
```

---

# Porter's Five Forces Analysis

```{r porters-chart}
porters$intensidad_score <- as.numeric(porters$intensidad_score)

# Translate force names and intensity levels
porters$force_en <- dplyr::recode(porters$fuerza,
  "Rivalidad entre Competidores" = "Competitive Rivalry",
  "Amenaza de Nuevos Entrantes"  = "Threat of New Entrants",
  "Poder de Proveedores"         = "Supplier Power",
  "Poder de Compradores"         = "Buyer Power",
  "Amenaza de Sustitutos"        = "Threat of Substitutes"
)
porters$intensity_en <- dplyr::recode(porters$nivel,
  "Muy Alta" = "Very High", "Alta" = "High",
  "Media"    = "Medium",   "Baja" = "Low"
)
porters$force_en <- factor(porters$force_en, levels = rev(porters$force_en))

ggplot(porters, aes(x = force_en, y = intensidad_score, fill = intensity_en)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = intensidad_score), hjust = 1.4,
            color = "white", fontface = "bold", size = 5) +
  scale_fill_manual(
    values = c("Very High" = colors[2], "High" = colors[5],
               "Medium"    = colors[3], "Low"  = colors[6]),
    name = "Intensity",
    breaks = c("Very High","High","Medium","Low")
  ) +
  scale_y_continuous(limits = c(0, 6), breaks = 1:5,
                     labels = c("Very Low","Low","Medium","High","Very High")) +
  coord_flip() +
  labs(
    title    = "Porter's Five Forces — Custom Market Research Provider",
    subtitle = "Qualitative competitive position assessment | Based on Miller (2008)",
    x = NULL, y = "Force Intensity"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title         = element_text(face = "bold", size = 14, color = "#1A1A2E"),
    plot.subtitle      = element_text(color = "gray40", size = 10),
    legend.position    = "bottom",
    panel.grid.major.y = element_blank()
  )
```

```{r porters-table}
porters %>%
  transmute(
    Force          = force_en,
    Intensity      = intensity_en,
    `Key Factors`  = descripcion
  ) %>%
  kable(align = c("l","c","l"),
        caption = "Porter's Five Forces Summary | Custom Research Provider") %>%
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = TRUE) %>%
  column_spec(2, bold = TRUE) %>%
  row_spec(0, background = colors[1], color = "white", bold = TRUE)
```

---

# Traditional vs. Digital Research Methods

## Method Usage Rate

```{r methods-usage}
methods$pct_uso <- as.numeric(methods$pct_uso)

# Translate method names and types
methods$method_en <- dplyr::recode(methods$metodo,
  "Encuesta Online"             = "Online Survey",
  "Entrevista Online (webcam)"  = "Online Interview (Webcam)",
  "Encuesta por Teléfono"       = "Phone Survey",
  "Entrevista Face-to-Face"     = "Face-to-Face Interview",
  "Focus Group Presencial"      = "In-Person Focus Group",
  "Encuesta por Correo"         = "Mail Survey"
)
methods$type_en <- dplyr::recode(methods$tipo,
  "Digital"     = "Digital",
  "Tradicional" = "Traditional"
)
methods$method_en <- factor(methods$method_en,
                            levels = methods$method_en[order(methods$pct_uso)])

ggplot(methods, aes(x = method_en, y = pct_uso, fill = type_en)) +
  geom_col(width = 0.65) +
  geom_text(aes(label = paste0(pct_uso, "%")),
            hjust = -0.15, fontface = "bold", size = 3.8) +
  scale_fill_manual(values = c("Digital" = colors[1], "Traditional" = "gray60"),
                    name = "Type") +
  scale_y_continuous(limits = c(0, 100)) +
  coord_flip() +
  labs(
    title    = "Most Used Research Methods (2022)",
    subtitle = "% of researchers using the method regularly | Source: Statista / ESOMAR",
    x = NULL, y = "% Usage"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title         = element_text(face = "bold", size = 14, color = "#1A1A2E"),
    plot.subtitle      = element_text(color = "gray40", size = 10),
    legend.position    = "bottom",
    panel.grid.major.y = element_blank()
  )
```

## Revenue by Service Type

```{r revenue-service}
rev_service$revenue_pct <- as.numeric(rev_service$revenue_pct)

# Translate service names and categories
rev_service$service_en <- dplyr::recode(rev_service$servicio,
  "Online/Mobile Cuantitativo" = "Online/Mobile Quantitative",
  "Reportes & Dashboards"      = "Reports & Dashboards",
  "Web Analytics & Online Traffic" = "Web Analytics & Online Traffic",
  "Online/Mobile Cualitativo"  = "Online/Mobile Qualitative",
  "Otros Servicios"            = "Other Services"
)
rev_service$category_en <- dplyr::recode(rev_service$categoria,
  "Digital" = "Digital", "Híbrido" = "Hybrid", "Mixto" = "Mixed"
)
rev_service$service_en <- factor(rev_service$service_en,
  levels = rev_service$service_en[order(-rev_service$revenue_pct)])

ggplot(rev_service, aes(x = service_en, y = revenue_pct, fill = category_en)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = paste0(revenue_pct, "%")),
            vjust = -0.5, fontface = "bold", size = 4) +
  scale_fill_manual(
    values = c("Digital" = colors[1], "Hybrid" = colors[3], "Mixed" = "gray70"),
    name = "Category"
  ) +
  scale_y_continuous(limits = c(0, 42)) +
  labs(
    title    = "Revenue Distribution by Service Type (2022)",
    subtitle = "Digital services dominate revenue generation | Source: Statista",
    x = NULL, y = "% of Total Revenue"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title         = element_text(face = "bold", size = 14, color = "#1A1A2E"),
    plot.subtitle      = element_text(color = "gray40", size = 10),
    legend.position    = "bottom",
    panel.grid.major.x = element_blank()
  )
```

## Survey Response Rates: Historical Decline & Comparison

```{r response-rates}
# Use only the three rate columns + year to avoid pivot conflicts
resp_clean <- response_hist %>%
  select(year, telefono_pct, online_pct, correo_pct) %>%
  mutate(across(c(telefono_pct, online_pct, correo_pct), as.numeric),
         year = as.integer(year))

resp_long <- resp_clean %>%
  pivot_longer(cols = c(telefono_pct, online_pct, correo_pct),
               names_to  = "method",
               values_to = "rate") %>%
  filter(!is.na(rate)) %>%
  mutate(method = dplyr::recode(method,
    "telefono_pct" = "Phone",
    "online_pct"   = "Online",
    "correo_pct"   = "Postal Mail"
  ))

p1 <- ggplot(resp_long, aes(x = year, y = rate, color = method, group = method)) +
  geom_line(linewidth = 1.5) +
  geom_point(size = 3) +
  scale_color_manual(
    values = c("Postal Mail" = colors[1], "Online" = colors[2], "Phone" = "gray50"),
    name = "Method"
  ) +
  scale_y_continuous(limits = c(0, 65), labels = function(x) paste0(x, "%")) +
  labs(
    title    = "Response Rate Trends Over Time",
    subtitle = "Source: Pew Research / BLS / ScienceDirect",
    x = "Year", y = "Response Rate"
  ) +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold", color = "#1A1A2E"),
        legend.position = "bottom", panel.grid.minor = element_blank())

# Current comparison
resp_comp_clean <- response_comp %>%
  mutate(across(c(tasa_media_pct, tasa_min_pct, tasa_max_pct), as.numeric))
resp_comp_clean$metodo <- factor(resp_comp_clean$metodo,
  levels = resp_comp_clean$metodo[order(resp_comp_clean$tasa_media_pct)])

p2 <- ggplot(resp_comp_clean,
             aes(x = metodo, y = tasa_media_pct,
                 ymin = tasa_min_pct, ymax = tasa_max_pct,
                 color = metodo)) +
  geom_pointrange(size = 1.2, linewidth = 1.2, show.legend = FALSE) +
  geom_text(aes(label = paste0(tasa_media_pct, "%")),
            vjust = -1, fontface = "bold", size = 4, show.legend = FALSE) +
  scale_color_manual(values = c(colors[6], colors[5], colors[3], colors[2])) +
  scale_y_continuous(limits = c(0, 90), labels = function(x) paste0(x, "%")) +
  coord_flip() +
  labs(
    title    = "Response Rate Range by Method",
    subtitle = "Dot = mean; line = typical range",
    x = NULL, y = "Response Rate (%)"
  ) +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold", color = "#1A1A2E"),
        panel.grid.major.y = element_blank())

p1 + p2 + plot_layout(widths = c(1.4, 1))
```

---

# AI Adoption in Marketing Research

## AI Adoption by Business Function (2023 vs. 2024)

```{r ai-function}
# Translate function names, then select to avoid column conflicts
ai_fn <- ai_function %>%
  mutate(
    pct_2023   = as.numeric(pct_2023),
    pct_2024   = as.numeric(pct_2024),
    function_en = dplyr::recode(funcion,
      "IT & Tecnología"          = "IT & Technology",
      "Marketing & Ventas"       = "Marketing & Sales",
      "Operaciones de Servicio"  = "Service Operations",
      "Desarrollo de Producto"   = "Product Development",
      "Finanzas"                 = "Finance",
      "RRHH"                     = "HR"
    )
  ) %>%
  select(function_en, pct_2023, pct_2024)

ai_long <- ai_fn %>%
  pivot_longer(cols = c(pct_2023, pct_2024),
               names_to  = "yr",
               values_to = "pct_val") %>%
  mutate(yr = dplyr::recode(yr, "pct_2023" = "2023", "pct_2024" = "2024"))

ai_long$function_en <- factor(ai_long$function_en,
  levels = ai_fn$function_en[order(ai_fn$pct_2024)])

ggplot(ai_long, aes(x = function_en, y = pct_val, fill = yr)) +
  geom_col(position = "dodge", width = 0.65) +
  geom_text(aes(label = paste0(pct_val, "%")),
            position = position_dodge(width = 0.65),
            hjust = -0.15, size = 3.5, fontface = "bold") +
  scale_fill_manual(values = c("2023" = "gray70", "2024" = colors[1]), name = "Year") +
  scale_y_continuous(limits = c(0, 46)) +
  coord_flip() +
  labs(
    title    = "AI Adoption by Business Function (2023 vs. 2024)",
    subtitle = "% of companies applying AI per function | Source: McKinsey Global AI Survey",
    x = NULL, y = "% of Companies"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title         = element_text(face = "bold", size = 14, color = "#1A1A2E"),
    plot.subtitle      = element_text(color = "gray40", size = 10),
    legend.position    = "bottom",
    panel.grid.major.y = element_blank()
  )
```

## AI in Marketing Research: Key Metrics

```{r ai-kpis}
ai_kpis$pct <- as.numeric(ai_kpis$pct)

# Translate indicator names
ai_kpis$indicator_en <- dplyr::recode(ai_kpis$indicador,
  "Investigadores que usan IA regularmente"              = "Researchers using AI regularly",
  "Organizaciones que planean invertir en IA"            = "Orgs planning to invest in AI (2025)",
  "Investigadores confiados usando IA"                   = "Researchers confident using AI",
  "Marketers que usaron ≥1 herramienta IA"              = "Marketers using ≥1 AI tool (2024)",
  "Empresas con IA integrada en estrategia core"         = "Companies with AI in core strategy",
  "Investigadores que usan datos sintéticos"             = "Researchers using synthetic data",
  "Adopción IA en Asia-Pacífico & Japón"                = "AI adoption — Asia-Pacific & Japan",
  "Adopción IA en Norteamérica"                         = "AI adoption — North America"
)
ai_kpis$indicator_en <- factor(ai_kpis$indicator_en,
  levels = ai_kpis$indicator_en[order(ai_kpis$pct)])

ggplot(ai_kpis, aes(x = indicator_en, y = pct, fill = pct)) +
  geom_col(width = 0.65, show.legend = FALSE) +
  geom_text(aes(label = paste0(pct, "%")),
            hjust = -0.15, fontface = "bold", size = 4) +
  scale_fill_gradient(low = colors[3], high = colors[2]) +
  scale_y_continuous(limits = c(0, 98)) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 38)) +
  coord_flip() +
  labs(
    title    = "AI in Marketing Research: Key Indicators",
    subtitle = "Source: Qualtrics, HubSpot, PwC, ESOMAR (2024–2025)",
    x = NULL, y = "% of Respondents"
  ) +
  theme_minimal(base_size = 11) +
  theme(
    plot.title         = element_text(face = "bold", size = 14, color = "#1A1A2E"),
    plot.subtitle      = element_text(color = "gray40", size = 10),
    panel.grid.major.y = element_blank(),
    axis.text.y        = element_text(size = 9.5)
  )
```

## AI in Marketing Market Size Forecast (2021–2028)

```{r ai-market}
ai_market$valor_bn <- as.numeric(ai_market$valor_bn)
ai_market$year     <- as.integer(ai_market$year)
ai_market$type_en  <- dplyr::recode(ai_market$tipo,
  "Real/Estimado" = "Actual / Estimated",
  "Proyección"    = "Forecast"
)

ggplot(ai_market, aes(x = year, y = valor_bn, fill = type_en)) +
  geom_col(width = 0.75) +
  geom_text(aes(label = paste0("$", valor_bn, "B")),
            vjust = -0.5, fontface = "bold", size = 3.8) +
  scale_fill_manual(
    values = c("Actual / Estimated" = colors[1], "Forecast" = colors[3]),
    name = NULL
  ) +
  scale_y_continuous(limits = c(0, 125),
                     labels = dollar_format(suffix = "B", prefix = "$")) +
  scale_x_continuous(breaks = 2021:2028) +
  labs(
    title    = "Global AI in Marketing Market Size (2021–2028)",
    subtitle = "Projected CAGR: 36.6% | Source: SEO.com / The Business Research Company",
    x = "Year", y = "Market Value (USD Billions)"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title         = element_text(face = "bold", size = 14, color = "#1A1A2E"),
    plot.subtitle      = element_text(color = "gray40", size = 10),
    legend.position    = "bottom",
    panel.grid.major.x = element_blank()
  )
```

---

# Summary & Conclusions

```{r kpis-table}
# Translate indicator names for summary table
kpis_summary$indicator_en <- dplyr::recode(kpis_summary$indicador,
  "Revenue global de la industria"              = "Global industry revenue",
  "Crecimiento 2021-2024"                       = "Growth 2021–2024",
  "Participación métodos digitales en revenue"  = "Digital methods share of revenue",
  "Investigadores que usan IA regularmente"     = "Researchers using AI regularly",
  "Mercado IA en marketing"                     = "AI in marketing market size",
  "Proyección IA en marketing"                  = "AI in marketing forecast",
  "Organizaciones usando IA en ≥1 función"      = "Orgs using AI in ≥1 function",
  "Tasa de respuesta online promedio"           = "Average online survey response rate",
  "Encuestas completadas desde móvil"           = "Surveys completed from mobile"
)
kpis_summary$unit_en <- dplyr::recode(kpis_summary$unidad,
  "Porcentaje"    = "Percentage",
  "USD Billones"  = "USD Billions"
)

kpis_summary %>%
  mutate(
    Value = paste0(valor,
      ifelse(unit_en == "Percentage",  "%",
      ifelse(unit_en == "USD Billions", "B USD", "")))
  ) %>%
  transmute(
    Indicator = indicator_en,
    Value     = Value,
    Year      = year,
    Source    = fuente
  ) %>%
  kable(align = c("l","c","c","c"),
        caption = "Key KPIs — Marketing Research & Data Science Industry") %>%
  kable_styling(bootstrap_options = c("striped","hover","condensed","responsive"),
                full_width = TRUE) %>%
  column_spec(2, bold = TRUE, color = colors[2]) %>%
  column_spec(4, color = "gray50", italic = TRUE) %>%
  row_spec(0, background = colors[1], color = "white", bold = TRUE)
```

## Key Findings

**1. The industry is growing rapidly**
Global market research revenue rose from \$29.5B in 2009 to \$140B in 2024 — a sustained
expansion driven by digitalization and rising demand for competitive intelligence.

**2. High competitive pressure (Porter)**
Custom research providers operate in a highly competitive market with low barriers to entry.
Differentiation through specialized expertise and technology is the only sustainable path.

**3. Digital methods now dominate**
Online methods account for 85% of researcher usage and 35% of industry revenue. Traditional
methods (phone, face-to-face) continue their long-term decline.

**4. AI: from optional tool to strategic necessity**
47% of researchers already use AI regularly, and 83% plan to invest in it by 2025.
The AI-in-marketing market will grow from \$47B (2025) to \$107B (2028).

**5. Response rates remain a persistent challenge**
Despite digital growth, online surveys average only a 44% response rate. Instrument design
and precise population targeting are the most critical improvement levers.

---

```{r hypothesis, echo=FALSE, results='asis'}
cat('
---

## Hypothesis

**"Marketing research firms that shift their value proposition from data collection to data
interpretation — leveraging digital tools and AI — will achieve sustainable competitive
advantage, while those anchored to traditional primary research methods will face structural
decline."**

---

### Theoretical Foundation

This hypothesis builds directly on Miller\'s argument that firms failed by defining themselves
by *how* they collected data rather than the *value* they delivered. Porter\'s Five Forces
reinforces it: in a market with high rivalry and low barriers to entry, the only escape from
price competition is meaningful differentiation through expertise and technology.

---

### What the Data Supports

- **Growth ≠ survival.** The industry grew 380% from 2009 to 2024, but Porter\'s analysis
shows this growth is not shared equally — it rewards differentiators, not the industry as a whole.

- **Traditional methods are in structural decline.** Phone survey response rates collapsed
from 36% to 5% in two decades. Firms still investing in traditional data collection are
building on a shrinking foundation.

- **AI is becoming the baseline, not the differentiator.** With 47% of researchers already
using AI and 83% planning to invest by 2025, firms that adopt late will use AI just to
keep up — not to lead.

- **Quality gaps create opportunity.** A 44% online response rate means volume and convenience
alone do not solve the research quality problem — that gap is exactly where human expertise
and rigorous methodology still create irreplaceable value.

---

### Bottom Line

The firms that survive are not those who do research *cheaper* — they are those who deliver
*smarter intelligence*. The data, the book, and Porter all point to the same conclusion:
in this industry, value is created at the interpretation layer, not the collection layer.

---
')
```
---

```{r ai-revolution, echo=FALSE, results='asis'}
cat('
---

## AI is Revolutionizing Marketing Research

---

### AI in Business Today

Artificial Intelligence is no longer a future concept — it is actively reshaping how
businesses operate right now. According to McKinsey (2024), **78% of organizations**
already use AI in at least one business function, up from just 55% a year before.
Companies are not experimenting anymore — they are deploying.

The numbers tell the story clearly:

- The global AI market reached **$638B in 2024** and is projected to hit **$1.81 trillion by 2030**
- Businesses using AI in marketing and sales report **5–10% revenue growth** directly linked to it
- **92% of firms** plan to increase their AI budgets within the next three years
- AI tools save marketing teams an average of **2.5 hours per day** per employee

AI is now present in every major business function — from finance and HR to operations
and customer service. But perhaps nowhere is its impact more transformative than in
**marketing research.**

---

### How AI is Changing Marketing Research Specifically

Traditional marketing research was slow, expensive, and limited by human capacity —
you could only interview so many people, analyze so many surveys, and process so much data.
AI removes those constraints entirely.

**Speed.** Tasks that used to take weeks — fielding a survey, cleaning data, running
analysis, writing a report — can now be compressed into hours. AI-powered platforms
like Qualtrics and Kantar\'s new insights engine deliver real-time consumer intelligence
that updates continuously rather than in quarterly reports.

**Scale.** AI can analyze millions of social media posts, customer reviews, and online
conversations simultaneously — a form of passive, always-on research that was simply
impossible before. This transforms research from a project into a continuous feed
of intelligence.

**Synthetic Data.** One of the most disruptive developments is the rise of synthetic
data — AI-generated respondents that simulate real consumer behavior. Already
**69% of researchers** are incorporating synthetic data into their work, allowing
firms to test hypotheses without recruiting a single real participant.

**Predictive Intelligence.** AI does not just describe what happened — it predicts
what will happen. Predictive analytics models now allow firms to anticipate consumer
trends, simulate market scenarios, and recommend strategic actions before a problem
even surfaces.

---

### What This Means for the Industry

The data in this analysis makes the stakes clear. The AI-in-marketing market is
growing at a **36.6% annual rate**, from $47B in 2025 to a projected $107B in 2028.
With **83% of research organizations** planning to invest in AI by 2025, it is
rapidly shifting from competitive advantage to baseline expectation.

The firms that embrace AI as an interpretation and intelligence tool — not just
an automation shortcut — will define the next era of marketing research.
The firms that do not will find themselves exactly where Miller warned:
defined by what they do, not the value they create.

> *"AI does not replace the researcher. It removes the ceiling on what a
> researcher can do."*

---
')
```
---

# Discussion Questions & Answers

---

**Q1. The industry grew 380% from 2009 to 2024. What forces drove this and will it continue?**

**A:** The main drivers were the rise of digital data, e-commerce, social media, and the shift 
to scalable online research methods that lowered costs for both buyers and sellers. Globalization 
also pushed firms to understand new markets. Future growth will likely slow — the projected CAGR 
of 4.6% through 2030 is much more moderate than the explosive 2021–2024 pace, which was partly 
inflated by post-pandemic digital transformation and early AI investment.

---

**Q2. Competitive Rivalry is rated Very High with thin margins. If you were launching a research 
firm today, what would your strategy be?**

**A:** You cannot compete on price or breadth against established players. The winning move is 
specialization — either by industry (become the go-to firm for healthcare or fintech research), 
by methodology (build proprietary AI tools that generate insights faster), or by owning a unique 
respondent community no competitor can replicate. The core lesson from the analysis is that firms 
defined by *what they do* (surveys, focus groups) die. Firms defined by the *value they add* 
(insight, strategy, foresight) survive.

---

**Q3. Online surveys have 85% adoption but only a 44% response rate. Does high adoption mean 
high quality?**

**A:** No — adoption and quality are very different things. The ease and low cost of online 
surveys explains the 85% adoption, but a 44% response rate means over half the target population 
isn't responding, which creates serious non-response bias. The people who respond may 
systematically differ from those who don't, skewing results in ways researchers may not detect. 
This is precisely where professional expertise still matters over DIY tools — rigorous sampling 
design and bias testing are not built into a SurveyMonkey account.

---

**Q4. AI adoption is 58% in Asia-Pacific vs. 39% in North America. What explains this gap?**

**A:** Asia-Pacific markets have leapfrogged older infrastructure in many cases, adopting 
AI-native platforms without legacy systems slowing them down. Intense competitive pressure in 
fast-growing economies also makes AI feel more urgent. In North America, established firms with 
large workforces and entrenched methodologies are slower to cannibalize their own processes, and 
data privacy regulations add friction. That said, 83% of North American organizations plan to 
invest in AI soon — the gap is likely temporary.

---

**Q5. The reading says firms got "ensnared in the trappings of primary research." Has the 
industry moved past that problem?**

**A:** Partially, but the risk remains. The data shows a clear shift — digital methods now 
represent 35% of revenue and 85% of researcher usage, and AI adoption is accelerating. Firms 
are clearly moving beyond defining themselves purely by data collection. However, with thousands 
of competitors and low barriers to entry, many mid-size firms still compete on methodology rather 
than insight value. The ones investing in AI, proprietary data assets, and specialized expertise 
are moving in the right direction — the ones that aren't are still trapped in the same pattern 
the reading warned about.

---
```{r ai-reflection, echo=FALSE, results='asis'}
cat('
---

## AI-Assisted Development: Reflections

---

### How We Used AI

During the development of this R Markdown analysis, we used **ChatGPT** and **Claude**
as support tools. They helped us generate `ggplot2` chart templates, debug cryptic error
messages, and structure the narrative sections like the hypothesis and discussion questions.

The most valuable use was debugging — when `pivot_longer()` threw a duplicate column name
error, pasting it into Claude produced the root cause and a fix in seconds.

---

### What AI Got Wrong

AI was not a plug-and-play solution. Key issues we ran into:

- Generated code that **looked correct but would not run** — wrong argument names,
deprecated functions, incompatible combinations.
- **Lost context** in long sessions and started contradicting earlier code decisions.
- Gave **wrong answers confidently** — with no signal that it was uncertain.

Every single AI-generated code block had to be tested and verified manually before use.

---

### The Bottom Line

> *AI is a skilled assistant, not an expert.*
> It speeds up execution — but you still need to do the thinking.

The best workflow we found: **think first, use AI to execute faster, verify everything.**

---

### Class Discussion

- Have you used AI for coding or analysis tasks? Did it save time or create more problems?
- Where do you think the line is between using AI as a tool vs. relying on it too much?

---
')
```

# References

- ESOMAR. (2024). *Global Market Research 2024 Report*. https://shop.esomar.org
- Statista. (2024). *Market Research Industry — Statistics & Facts*. https://www.statista.com
- McKinsey & Company. (2025). *The State of AI in 2025*. https://www.mckinsey.com
- Qualtrics. (2024). *Market Research Trends Report 2024*. https://www.qualtrics.com
- Wu, M.-J. et al. (2022). Response rates of online surveys: A meta-analysis.
  *Computers in Human Behavior Reports*, 7. https://doi.org/10.1016/j.chbr.2022.100206
- Miller, T. W. (2015). *Modeling Techniques in Predictive Analytics*. Pearson.
- Porter, M. E. (1980). *Competitive Strategy*. Free Press.
- The Business Research Company. (2024). *Market Research Services Global Market Report 2024*.
